\newif\ifccs
\ccsfalse

\ifccs
\input{preamble_ccs.tex}
\else
\input{preamble.tex}
\fi



\newif\ifdesperatetime
%\desperatetimetrue

\graphicspath{{images/}}

\begin{document}
\title{\name: Root-of-Trust for IO \\ in Compromised Platforms}

\ifccs
\else
\maketitle
\fi

\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
 
%Recent exploitations, hardware-based malware and privacy breaches show that the concept of a powerful adversary who can completely compromise a host (computer) system (hardware, operating system, and installed applications) is not far fetched. \emph{Security} and \emph{safety-critical} \emph{remote} applications such as e-voting, financial transitions, various industrial control systems, medical devices, and home automation systems rely upon user interaction that is typically transmitted through web applications. A compromised host can either observe or manipulate these data. And by doing so, it can cause catastrophic failure in the safety-critical systems, theft of identity and financial information, thus making this problem a uniquely challenging one.

\emph{Security} and \emph{safety-critical} remote applications such as e-voting, online banking, industrial control systems, medical devices, and home automation systems rely upon user interaction that is typically performed through web applications. Trusted path to such remote systems is critical in the presence of an attacker that controls the computer that the user operates. Such a powerful attacker can observe and modify any IO data without being detected by the user or the server. 
%Many proposals in the literature try to address the integrity and confidentiality of the IO operations in this attacker model. 
%However, none of them provides a secure and generic solution. 
We investigate the security of previous research proposals that address this problem and observe several drawbacks that make them vulnerable to advance UI manipulation attacks.
%find subtle attacks on recent research proposals and 
Based on these observation we define the requirements for secure IO operation in the presence of a compromised host.
%through compromised host: i) without preserving both output and input integrity, none of them can be achieved, and ii) all the input modalities are needed to be protected.    

We propose \name, a system that ensures the integrity and confidentiality of the user's IO employing a trusted low-TCB device that sits between the attacker-controlled host and the IO devices. Therefore, \name device can intercept the display signal and user inputs from the keyboard and mouse. Furthermore, it can overlay secure UI on top of the HDMI frames generated by the untrusted host. \name integrates well in the existing infrastructure, it requires small changes in the server-side, works with any browser without installing any additional software, and does not change significantly the user experience. 
Finally, we implement a prototype of \name which is a plug-and-play device and evaluate its performance.
%All such overlays and user input are authenticated.
%\name, our proposed solution is based on the above identified properties, and it ensures the integrity and confidentiality of user's IO utilizing a trusted low-TCB external device that sits between the attacker-controlled host and all the IO devices. Today's off-the-shelf commodity hardware could easily integrate \name with little or no changes into the system. \name intercepts the display signal \& user input, overlay secure UI on top of the display signal. All such overlays and user input are authenticated. Thus, \name provides a generic and usable trusted path for all IO devices. 

\end{abstract}


\ifccs
\maketitle
\else
\fi

\input{sections/intro}
\input{sections/background}
\input{sections/problemStatement}
\input{sections/approach}
\input{sections/systemDesign}
\input{sections/IOPrivacy}
\input{sections/securityAnalysis}
\input{sections/Prototype}
\input{sections/Evaluation}
%\input{sections/usecase}
\input{sections/relatedWork}
%\input{sections/attacks}
\input{sections/conclusion}


\ifccs
\bibliographystyle{ACM-Reference-Format}
\else
\bibliographystyle{IEEEtran}
\fi

\bibliography{references}

\appendix
\input{sections/appendix}

\end{document}
